---
title: "Eating Out"
author: "Th3b0yn3xtd00r"
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Does the frequency of outside eating habits vary among ethnicity?

## There were two years in which the General Social Survey asked about the frequency of eating out.
### Find those years and for the first year the question was asked download that years data in a stata format - its name will be "GSSxxxx.dta" where the xxxx is replaced by the year.  For example if the year was 1983 its name would be GSS1983.dta. Your assignment is to download the GSS yearly dataset for the first year the question was asked and then  write up the answer to the question by editing the  code block in line 31 to eval=TRUE and finish the job. 

$H_0$ There is no difference among the various races with frequency of eating out  
$H_A$ There is a statistical difference between at least two races with the frequency of eating out  


```{r include=FALSE,echo=FALSE}
source(file="fisherXY.R")
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
```
```{r, eval=TRUE, include=FALSE}
GSS <-readstata13::read.dta13(file="GSS1996.dta")
GSS <- droplevels(GSS)
mydata <- select(GSS,race,age,eatout)
mydata <- na.omit(mydata)
```



# Method
In order to interpret the data, the Categorical Numerical method is essential in determining which ethnicity eats out more frequently.

# Descriptive Results

## graphical results

```{r}
barchartGC(~race + eatout,data=mydata)
barchartGC(~race + eatout,data=mydata,type="percent")
```

The Bar chart above presents how "White" people eat out more frequently than "Black" people and "other" people.

## Numerical description


```{r}
table1 <- xtabs(~race + eatout,data=mydata)
rowPerc(table1)
colPerc(table1)
```

The results in this numerical description states and shows the frequency of eating out in white ethnicity as opposed to black and other ethnicity. Stating white ethnicity frequency of eating out is more than black and other ethnicity.

## inferential results

```{r}
chisq.test(table1)
chisqtestGC(table1)
fisherXY(mydata$race,mydata$eatout,printAll=T)
```

Chi squared test shows the P value 0.0008179, we see the number is so small that we reject the null hypothesis.
The fisher exact test for count data shows that the p value 0.001208 is also very small that we reject the null hypothesis.

# Disscussion and conclusion
Based on the results, we reject the null hypothesis since the p value is so small. Considering the p value is 0.0008179, I conclude there is a difference in the frequency of eating out based on white ethnicity eating out.


